Analysis

### 2018-11-13 reports/analysis_pilot.Rmd
polishing of the outputs for OPAM

@@

```{r}
p <- df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  xlab("Quintile") + 
  theme(text = element_text(size=14))
p
ggsave(here::here("plots", "opam_figure.eps"), p, width = 6, height = 6)

>>>>

plots_dir <- here::here("plots")

if(!dir.exists(plots_dir)) {
  dir.create(plots_dir)
}

@@

```{r}
p <- df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) +
  ylab("Perc. correct") +
  theme(text = element_text(size=18)) +
  scale_x_continuous("Quintile", breaks = c(2,3,4), labels = c("2","3","4"))
p
ggsave(file.path(plots_dir, "opam_figure.eps"), p, width = 6, height = 6)
